Phylogenetics and the human microbiome.

### 2014-06-28 sbreview.tex
Few more fixes.

\newcommand{\pdLegend}{
    Unweighted phylogenetic diversity (PD, left) and an abundance-weighted PD measure (right), where taxa present in a sample are shown as circles and abundances are shown as the size of the circles.
    Unweighted PD takes the sum of the branch lengths connecting samples.
    Abundance-weighted measures take a weighted sum of branch lengths where weight is determined in some way by the abundance of the taxa on either side of the branch: if we give edges width according to their weight, the abundance-weighted measure can be thought of as the sum of the total area of the edges.
    One such abundance-weighted measure simply takes the absolute value of the difference of the total taxon abundance on one side compared to the other.
}
\forarxiv{
\begin{wrapfigure}[26]{r}{2.2in}
  % \capstart
  \vspace{-25pt}
  \begin{center}
    \includegraphics[width=2.2in]{figures/pd.pdf}
  \end{center}
  \vspace{-10pt}
  \caption{\pdLegend}
  \label{fig:pd}
\end{wrapfigure}
}

Phylogenetic diversity (PD) measures use the structure and branch lengths of a phylogenetic tree to measure the diversity of a sample (Fig.~1).
The (unweighted) PD of a set of taxa $S$ in an unrooted phylogenetic tree is simply the total of the lengths of the branches that sit between taxa in $S$ \citep{faith1992conservation}.
It quantifies the ``amount of evolution'' contained in the evolutionary history of those taxa.
Unweighted PD has been applied to some 16S survey data \citep{lozupone2007global,costello2009bacterial} and to metagenomic reads in a set of marker genes \citep{kembel2011phylogenetic}.

>>>>

\newcommand{\pdLegend}{
    Unweighted phylogenetic diversity (PD, left) and an abundance-weighted PD measure (right), where taxa present in a sample are shown as circles and abundances are shown as the size of the circles.
    Unweighted PD takes the total length of branches sitting between tree tips represented in a sample.
    Abundance-weighted measures take a weighted sum of branch lengths where weight is determined in some way by the abundance of the taxa on either side of the branch: if we give edges width according to their weight, the abundance-weighted measure can be thought of as the sum of the total area of the edges.
    One such abundance-weighted measure simply takes the absolute value of the difference of the total read abundance on one side compared to the other.
}
\forarxiv{
\begin{wrapfigure}[26]{r}{2.2in}
  % \capstart
  \vspace{-25pt}
  \begin{center}
    \includegraphics[width=2.2in]{figures/pd.pdf}
  \end{center}
  \vspace{-10pt}
  \caption{\pdLegend}
  \label{fig:pd}
\end{wrapfigure}
}

Phylogenetic diversity (PD) measures use the structure and branch lengths of a phylogenetic tree to measure the diversity of a sample (Fig.~1).
The (unweighted) PD of a set of taxa $S$ in an unrooted phylogenetic tree is simply the total length of the branches that sit between taxa in $S$ \citep{faith1992conservation}.
It quantifies the ``amount of evolution'' contained in the evolutionary history of those taxa.
Unweighted PD has been applied to some 16S survey data \citep{lozupone2007global,costello2009bacterial} and to metagenomic reads in a set of marker genes \citep{kembel2011phylogenetic}.
